Inferring Lensing Mass in the Universe \\ from Photometric Catalog Data

### 2012-10-08 doc/paper-lcr.tex
refs added to intro, figs tidied away

This fact makes gravitational lensing a potentially important source of
systematic error for any estimate of luminosity or distance, an issue addressed
for \eg type Ia supernovae by \citet[][]{Holz+Wald1998,Linder+Holz2004} and for high
redshift galaxies by \tom{which paper?} \citet{Loeb} among others. In time delay lens cosmography
the effect can be particularly important. \citet{Suyu++2010} found that  the
lensing effect of mass structures along the (unusually over-dense)  line of
sight to the quadruply-imaged radio source B1608$+$656, the so-called ``external
convergence,'' was the dominant source of uncertainty in the inferred
cosmological parameters.

How can we correct for the line of sight lensing error, and make accurate
measurements through the Universe? As \citeauthor{Linder+Holz2004} noted, when inferring
global quantities (such as the cosmological parameters), averaging the results
from a large number of independent objects will tend to reduce the error, as the
ensemble-averaged convergence approaches zero for an unbiased sample
\citep{xxx}. If the sample is biased, however, some residual systematic error
will remain while the statistical uncertainty decreases -- and this will be the
case for any sample selected by the brightness of the lensed object, or any
other quantity that depends on $\xkappa$. The latter class includes time delay
lenses, which are detected based on the separation of their images, which
increases with $\kappa$. Large samples of lenses are expected to be discovered
in the next decade in ground-based optical imaging surveys
\citep{Oguri+Marshall2010} -- but these samples will be image separation-limited,
due to the surveys' relatively poor ($\sim 1$~arcsec) image quality. Some of the
current sample of known time delay lenses were detected in surveys like this: we
might expect them to be somewhat biased towards high values of $\xkappa$.

There are two broad approaches one could take at this point. First, one could
seek to characterise the lensed objects' selection function, and use this
understanding to derive a suitable correction to cosmological parameters
inferred assuming no $\xkappa$ at all. To do this, one needs information about
the unlensed population of objects, and the population of lenses, and how the
objects were detected -- or to infer these hierarchically during the analysis.
Alternatively, one could simply accept all lenses provided, regardless of their
selection, and try to use any additional information that is available to
estimate the external convergence in each system on a case by case basis, and
hence optimize their joint analysis to produce a better-constrained result. In
this work we follow the second approach, and use measurements of the positions,
magnitude and colours of galaxies close to time delay lens lines of sight to try
to infer the external convergence at the lens position.

Previous attempts at reconstructing the line of sight mass distribution in
strong lens fields have focused on spectroscopic surveys to ascertain group
membership, and on understanding the external shear apparently required by the
strong lens models.  The probability density function (PDF) $\Pr(\xkappa)$ is
the target for any reconstruction analysis, and the key quantity for any
ensemble analysis, since by marginalising over it we can correctly propagate
the uncertainties due to weak lensing by line of sight mass structure. 
\todo{Tom, Matt}{More needed here. Previous work on environments: Keeton,
Zabludoff,Auger, Momcheva, Wong, others.}
Most recently, \citet{Wong++2011} ran Monte
Carlo reconstructions of the mass in nine lens fields, and compared the
resulting predicted shear distributions with the lens model external shear.
Their simulations show most of  the shear being generated by bright galaxies
within 2~arcminutes of the lens, and that both line of sight structures and
the group of galaxies in each lens plane contribute significant proportions of
the shear. The significant discrepancies between the lens model shear and the
Monte Carlo predictions are attributed to both the environment modelling and
the strong lens modelling itself.

These observational investigations have provided very useful insight into the
problem.  Coming from the opposite direction, large numerical simulations have
been used to predict, from first principles the distribution of likely
external shears and convergences along strong lens lines of sight. \todo{Phil}{More
needed here. Holder \& Schechter, Dalal \& Watson}. \citet{Hilbert++2009}
performed ray-tracing experiments through the Millenium Simulation \citep{Springel++2005}, generating
a predicted $\xkappa$ at every position in a simulated sky. The first step
towards using this excellent calibration resource was taken by
\citet{Suyu++2010}, who selected Millenium lines of sight that a) were found
to contain a strong lens and b) had comparable apparent galaxy overdensity in
a 45 arcsec radius aperture down to $i < 24$. This overdensity could be
compared to the overdensity of the B1608$+$656 line of sight
\citep{Fassnact++2011}, and hence an estimate of  $\Pr(\xkappa)$ could be
made.

What has not been investigated before, but is the subject of this paper, is
the use of simulations to {\it calibrate} lightcone reconstruction methods.
Ray-tracing through the simulations gives a ``truth'' that we can attempt to
recover.  In this paper we use the Millenium Simulation mock galaxy catalogs
and ray-traced lensing effects to test the accuracy of line of sight mass
reconstructions. Probabilistically ssigning mass and redshift to every
observed galaxy in the field around a time delay lens, we generate Monte Carlo
sample line of sight mass distributions, and estimate the external convergence
due to each one. This gives us a $\Pr(\xkappa)$ that can be propagated into
further joint inferences. We focus on time delay lens cosmography, and
quantify our results in terms of the uncertainty on the mean time delay
distance to a test sample of $N$ lenses (where for clarity each lens has the
same deflector and source redshift, and the same lens model and time delay
uncertainty).

@@

Throughout this paper magnitudes are given in the AB system \citep{Oke74} and
we adopt the Millenium Simulation's ``concordance'' parameters for our reference cosmology, \ie
$h=0.73$, $\Omega_m=0.25$ and $\Omega_\Lambda=0.75$, where the symbols indicate
the Hubble Constant in units of 100 km s$^{-1}$ Mpc$^{-1}$ and the matter and
dark energy density of the Universe in units of the critical density
.%\citep[e.g.\ ][]{Kom++09}.

@@

Strong lenses sit in our real Universe -- they are not truely isolated;
there is some mass along the line of sight coming from intervening structures.
These structures may be physically associated with the lens e.g. other members
of a group or cluster, or they may be the result of chance alignments at any redshift. 
Whilst it is rare for three galaxies to line up well enough for both of the background sources
to be strongly lensed \citep{Gavazzi++2008,Collett++2012a}, the shear scale of dark matter halos
makes a partial alignment -- with the additional structure acting as a weak lens -- 
a near certainty, indeed \citet{Vale+White2003} and \citet{Hilbert++2007} find that there
are no empty lightcones in a realistic universe. These additional structures induce an external shear
which can be recovered in the mass-modelling of the lens, but they can also introduce a convergence that
is undetectable from the image positions, shapes and relative fluxes; {\it the mass sheet-degeneracy} \citep{Falco++1985}.

If the intrinsic source brightness changes, the observed brightness in each image does not change
simultaneously - there is a time delay, $\Delta t$, between the brightness change in
each image. Despite the invariance of the image positions and fluxes, under the addition
of an external convergence (and appropriate re-scaling of the lens potential) the relative Fermat potential between the images is {\it not}
invariant, and so the time delay changes. As such it is necessary to include $\kappax$
in the lens modelling, if cosmological parameters are to be estimated accurately and
precisely from observed time delays \citep{Suyu++2010}.

@@

Unphysically, if one integrates the density profile of an NFW profile, the total mass is divergent.
Similarly, if the universe is homogeneously populated with NFW halos, the projected surface mass along any
line of sight will also be divergant\footnote{At large radius, $\Sigma_{\rm
nfw} \propto R^{-2}$, but the differential number of halos centred within an
annulus of width $\dee R$ is given by $\dee N_{\rm annulus} \propto R \dee R$,
so  $\Sigma_{\rm total} \propto \int_{0}^{\infty} R^{-1} \dee R$, which
diverges logarithmically}. Since infinite mass is unphysical, the profile must
be truncated at some point. \todo{Tom}{Add notes on previous truncation results}. Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low; \citet{Nandra++2012} showed that the Universe's expansion can place an upper limit on the radius of NFW halos -- for cluster scale halos, this happens at around 25 times the NFW scale radius. In \Sref{sec:knownMh+z} we investigate how different truncations affect the recovered total convergence for a line of sight, using the truncated NFW profile of \citet{BMO}
\be\label{eq:bmoprofile}
\rho(r) = 
\frac{\rho_{\rm NFW} (r)}{1+\left(r/r_{t}\right)^2},
\ee
which is the same as the NFW profile in the limit that the truncation radius, $r_t$ goes to infinity. The convergence and shear for the BMO profile are given in Appendix \ref{appendix:halos}.

@@

We choose 100000 lines of sight from random positions in the catalogue, and for each line of sight we reconstruct the
convergences from every halo within 5 arcminutes and compare the reconstructed
$\kapparec$ with those from the ray tracing results. The standard deviation on $\kapparay$-$\kapparec$ is
shown in Figure \ref{fig:ScattervsTruncation} as a function of the radius at which the halo is truncated.
 It is clear from Figure \ref{fig:ScattervsTruncation} 
that as long as the truncation is greater than a few virial radii, the choice of truncation
radius does not broadly affect the scatter on $\kapparay-\kapparec$; from now on we choose 
to truncate the halos at $5 \Rhalo$. Since $\sigma\left(\kapparay-\kapparec\right)$ does not go to
zero, it is clear that out halo based prescription does not perfectly replicate the n-body results, we refer to this
 as the intrinsic error of the prescription.
 The intrinsic error has a standard deviation of $\sigi \sim 0.018$, although
this figure is inflated by a few outliers in the tails of $\pr\left(\kapparay-\kapparec\right)$. Such outliers would 
likely be rejected by their reconstructed shear not matching the shear of the lens model 
(see \citet{Wong++2011} for the practicalities of this);
 this makes our estimate of the intrinsic error pessimistic. We do not include any additional constraints on P($\kappax$), given prior knowledge of the external shear in this work.

\begin{figure}
\includegraphics[width=\columnwidth]{truncation_scatter.eps}
\caption[magcut]{The standard deviation in $\kapparec$ minus $\kapparay$ as a function of halo truncation radius in virial radii, using the truncated NFW profile of \citet{BMO}. In our models we truncate our halos at 5$R_{200}$}
\label{fig:ScattervsTruncation}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{perfectc.eps}
\caption[Biased?]{$\sumkappah$ verses $\kapparay$ for 100000 reconstructed lines of sight. $\sumkappah$ traces $\kapparay$, but with a non-zero offset which is due to the negative connvergence from voids. At fixed $\sumkappah$ the scatter in $\kapparay$ grows with $\sumkappah$.}
\label{fig:isitbiased}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{mag_scatter.eps}
\caption[magcut]{The 16, 50 and 84\% confidence intervals on $\kapparec$ minus $\kapparay$ as a function of the limiting $i$ band depth of the halo reconstruction. $\kapparec$ is given by $\sumkappah-\kappav$, where $\kappav$ is a constant such that $\left\langle\kapparec\right\rangle=0$. The majority of the constraining power comes from reconstructing halos with magnitudes between $18<i<24$}
\label{fig:magcut}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{radius_scatter.eps}
\caption[radius cut]{The 16, 50 and 84\% confidence intervals on $\kapparec$ minus $\kapparay$ as a function of the limiting radius (in arcminutes) beyond which halos are not reconstructed. The majority of the convergence comes from halos centred within an arcminute of the line of sight}
\label{fig:radcut}
\end{figure}

@@

We generate a stellar mass for each halo according to the stellar mass--halo mass relation of \citet{Behroozi++2010}. From this stellar mass we simulate 
an observed stellar mass by drawing a sample from $\pr(\log(M_{* \mathrm {obs}})|\log(M_{* \mathrm {true}}))$ which is given by \comments{ the product of the galaxy stellar mass function (GSMF) of \citet{Fontana2006} and} a Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$. Where a spectroscopic redshift exists stellar masses can be estimated with typical uncertainties of 0.15 dex \citep{xxx}, however with photometric redshifts stellar mass uncertainties are typically three times as large \citep{xxx}; we use $\sigma_{M_*}=0.15$ for halos with a spectroscopic redshift and $\sigma_{M_*}=0.45$ otherwise. \comments{The \citet{Fontana2006} GSMF is given by a Schechter function with redshift evolving parameters
\be
\label{eq:GSMF}
{\dee N \over \dee M_*} \propto \left(10^{(M_*-M_0(z))}\right)^{(1+\alpha(z))} \exp \left(-10^{(M_*-M_0(z))}\right)
\ee 
where $M_0(z)=11.16+0.17z-0.07z^2$ and $\alpha(z)=-1.18-0.082z$.} For photometric redshift errors we draw a redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take as a Gaussian of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where $z_{\rm spec}$ is the halo's true redshift in the \MS catalogue

@@

\begin{figure}
\includegraphics[width=\columnwidth]{cornerplot.eps}
\caption{68 \% and 95 \% contours of the joint distribution $\pr(\kapparay, \tilde\kappa_{\rm halos})$ given a mock reconstruction of our 40000 calibration lines of sight. $\tilde\kappa_{\rm halos}$ is the median of $\pr(\sumkappah)$ given a spectroscopic redshift for each halo. $\kapparay$ and $\tilde\kappa_{\rm halos}$ are strongly correlated, despite the blurring effect of uncertain halo masses.}
\label{fig:corner}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{widths.eps}
\caption{Widths of $\pr(\kappax)$ after applying our reconstruction of all halos down $to i=26$ and within 5 arcminutes of the line of sight. Results for 10000 lines of sight are shown. Green is for a reconstruction given perfect knowledge of halo mass and redshift, blue is for a reconstruction given a spectroscopic redshift for every halo, and red is for a reconstruction with photometric redshifts only. The dashed black line shows the width of the global $\pr(\kappax)$ distribution; the reconstruction process provides roughly a factor of 2 improvement for the majority of lines of sight. Spectroscopic redshifts improve the reconstruction, but at signifcant observational cost.}
\label{fig:width1}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{widths2.eps}
\caption{Widths of $\pr(\kappax)$ after a photometric reconstruction of all halos within different fields. The different field sizes and depths are given in the legend. As the field becomes smaller or shallower, fewer halos are being reconstructed and so the width of $\pr(\kappax)$ grows.}
\label{fig:width2}
\end{figure}

@@

The method we have outlined can also be used to estimate the external shear
along a line of sight. Shear is an observable that can be extracted from
strong lens modelling, however there is a degeneracy between internal and
external shear. Progress has been made in disentangelling external and
internal shear \citep[\eg][]{xxx} but there are still significant
uncertainties: \citet{Wong++2011} attempted to match the shear from strong lens
models with a reconstruction of the local lens group environment, but found a
tension between the strong lens model and the reconstruction of the
environment. Since \citet{Wong++2011} only reconstructed the local lens group,
rather than the full line of sight contribution, it is unclear whether the
external shear from lens models can be reconciled with a line of sight
reconstruction. {\it If} external shear can be measured, it provides an
additional constraint on which of the Millenium Simulation lines of sight are
similar to the reconstructed line of sight. \citet{Suyu++2012b} found that for RXJ1131 combining shear constriants with galaxy number count overdensity, gave a significantly different $\pr(\kappax|\gamma,N_{45})$ copmpared to the PDFfrom number count overdensity alone, $\pr(\kappax|N_{45})$.

@@

%\bibliographystyle{apj}
%\bibliography{references}

>>>>

This fact makes weak gravitational lensing a potentially important source of
systematic error for any estimate of luminosity or distance, an issue
raised for \eg 
type Ia supernovae by \citet[][]{Holz+Wald1998,Linder+Holz2004}, for
gamma ray bursts by \citet[][]{Oguri+Takahashi2006,Wang+Dai2011}, 
and for high redshift galaxies by \citet{BradacEtal2009}, among others. 
Along lines of sight containing strong gravitational lenses,
the effect has been found to be
particularly important, with foreground and background structures
having a significant effect on the inferred lensing cross-section
\citep[\eg][]{WongEtal2012} and distance ratios \citep[][]{DalalEtal2005}.
In time delay lens cosmography,
\citet{SuyuEtal2010} found that  the lensing effect of mass structures along the
(unusually over-dense)  line of sight to the quadruply-imaged radio source
B1608$+$656, the so-called ``external convergence,'' was the dominant source
of uncertainty in their 6\% measurement of Hubble's constant.

How can we correct for this weak lensing error, and make
accurate measurements through the Universe? When inferring global quantities
(such as the cosmological parameters), averaging the results from a large
number of independent objects will tend to reduce the error, as the
ensemble-averaged convergence approaches zero for an unbiased sample
\citep[\eg][]{Linder+Holz2004}. If the sample is biased, however, some
residual systematic error will remain while the statistical uncertainty
decreases -- and this will be the case for any sample selected by the
brightness of the lensed object, or any other quantity that depends on
$\xkappa$. The latter class includes time delay lenses, which could be
either detected or selected 
based on their image separations, magnifications or quadruple image
configurations, all of which either increase or become more likely with
increasing $\kappa$. Large
samples of lenses are expected to be discovered in the next decade in
ground-based optical imaging surveys \citep{Oguri+Marshall2010} -- but these
samples will be image separation-limited, due to the surveys' relatively poor
($\sim 1$~arcsec) image quality. Some of the current sample of known time
delay lenses were detected in surveys like this: we might expect them to be
somewhat biased towards high values of $\xkappa$.

There are two broad approaches one could take at this point. First, one could
seek to characterise the lensed objects' selection function, and use this
understanding to derive a suitable correction to cosmological parameters
inferred assuming no $\xkappa$ at all. As pointed out by  \citet[][among
others]{Oguri+Takahashi2006}, to do this one would need  information about the
unlensed population of objects, and the population of lenses, and how the
objects were detected -- or to infer these hierarchically during the analysis.
Alternatively, one could simply accept all lenses provided, regardless of
their selection, and try to use any additional information that is available
to estimate the external convergence in each system on a case by case basis,
and hence optimize their joint analysis to produce a better-constrained result
\citep[as suggested by][]{Keeton+Zabludoff2004}. In this work we follow this
second approach, and use measurements of the positions, magnitude and colours
of galaxies close to lens lines of sight to try to infer the
external convergence at the lens position.

Attempts to date at reconstructing the local and  line of sight mass
distribution in strong lens fields (what \citeauthor{WongEtal2011} call ``the
full environment'') have focused on photometric and  spectroscopic surveys to
detect galaxy groups and ascertain galaxies' membership,  and on understanding
the external shear apparently required by the strong lens models. Surveys by
\citet{Fassnacht+Lubin2002,AugerEtal2007,WilliamsEtal2006,MomchevaEtal2006}
all found groups of galaxies both hosting and lying  along the line of sight
to known gravitational lenses. Initial estimates of the effect of these
structures suggested the importance of assigning mass to both galaxy and group
halos, and to allowing for significant uncertainty in the centroids of group
halos. The probability density function (PDF) for the external convergence for
that lens, $\Pr(\xkappa)$, is the target for any reconstruction analysis, and
is the key quantity for any ensemble analysis, since by marginalising over it
we can correctly propagate the uncertainties due to weak lensing. Coming
closest to estimating this quantity from survey data, \citet{WongEtal2011} ran
Monte Carlo reconstructions of the mass in nine lens fields based on
\citeauthor{WilliamsEtal2006} and \citeauthor{MomchevaEtal2006}'s
photometric and spectroscopic measurements of galaxies close to the line of
sight, and compared the resulting predicted shear distributions with the
external shear demanded by the strong lens model. Their simulations show most
of the shear being generated by bright galaxies within 2~arcminutes of the
lens, and that both line of sight structures and the group of galaxies in each
lens plane contribute significant proportions of the shear. They find
significant discrepancies between the lens model shear and the Monte Carlo
predictions, and are unable to distinguish between the environment modelling
and the strong lens modelling as the cause of these discrepancies.

These observational investigations have provided very useful insight into the
problem.  Coming from a more theoretical direction, large numerical
simulations have been used to predict, from first principles, the distribution
of likely external shears and convergences along strong lens lines of sight. 
\citet{Holder+Schechter2003} and \citet{Dalal+Watson2004} carried out
ray-tracing calculations in N-body simulations to estimate the  distribution
of external shear values.  \citet{HilbertEtal2009} performed similar ray-tracing
experiments through the Millenium Simulation \citep{SpringelEtal2005},
generating a predicted $\xkappa$ at every position in a simulated sky. The
first step towards using this excellent calibration resource was taken by
\citet{SuyuEtal2010}, who selected Millenium Simulation lines of sight that a)
were found to contain a strong lens and b) had comparable apparent galaxy
overdensity in a 45 arcsec radius aperture down to $i < 24$. This overdensity
could be compared to the overdensity of the B1608$+$656 line of sight
\citep{FassnachtEtal2011}, and hence an estimate of  $\Pr(\xkappa)$ could be
made.

In this paper, we bring these observational and theoretical approaches
together and  use numerical simulations to {\it test and calibrate} a
reconstruction of the  external convergence. Ray-tracing through the
simulations gives a ``truth'' that we can attempt to recover.  In this paper
we use the Millenium Simulation mock galaxy catalogs and ray-traced lensing
effects to test the accuracy of line of sight mass reconstructions.
Probabilistically ssigning mass and redshift to every observed galaxy in the
field around a time delay lens, we generate Monte Carlo sample line of sight
mass distributions, and estimate the external convergence due to each one.
This gives us a $\Pr(\xkappa)$ that can be propagated into further joint
inferences. We focus on time delay lens cosmography, and quantify our results
in terms of the uncertainty on the mean time delay distance to a test sample
of $N$ lenses (where for clarity each lens has the same deflector and source
redshift, and the same lens model and time delay uncertainty).

@@

Throughout this paper magnitudes are given in the AB system and
we adopt the Millenium Simulation's ``concordance'' parameters for our reference cosmology, \ie
$h=0.73$, $\Omega_m=0.25$ and $\Omega_\Lambda=0.75$, where the symbols indicate
the Hubble Constant in units of 100 km s$^{-1}$ Mpc$^{-1}$ and the matter and
dark energy density of the Universe in units of the critical density
.%\citep[e.g.\ ][]{KomEtal09}.

@@

Strong lenses sit in our real Universe -- they are not truely isolated;
there is some mass along the line of sight coming from intervening structures.
These structures may be physically associated with the lens e.g. other members
of a group or cluster, or they may be the result of chance alignments at any redshift. 
Whilst it is rare for three galaxies to line up well enough for both of the background sources
to be strongly lensed \citep{GavazziEtal2008,CollettEtal2012a}, the shear scale of dark matter halos
makes a partial alignment -- with the additional structure acting as a weak lens -- 
a near certainty, indeed \citet{Vale+White2003} and \citet{HilbertEtal2007} find that there
are no empty lightcones in a realistic universe. These additional structures induce an external shear
which can be recovered in the mass-modelling of the lens, but they can also introduce a convergence that
is undetectable from the image positions, shapes and relative fluxes; {\it the
mass sheet-degeneracy} \citep{FalcoEtal1985}.

If the intrinsic source brightness changes, the observed brightness in each image does not change
simultaneously - there is a time delay, $\Delta t$, between the brightness change in
each image. Despite the invariance of the image positions and fluxes, under the addition
of an external convergence (and appropriate re-scaling of the lens potential) the relative Fermat potential between the images is {\it not}
invariant, and so the time delay changes. As such it is necessary to include $\kappax$
in the lens modelling, if cosmological parameters are to be estimated accurately and
precisely from observed time delays \citep{SuyuEtal2010}.

@@

Unphysically, if one integrates the density profile of an NFW profile, the total mass is divergent.
Similarly, if the universe is homogeneously populated with NFW halos, the projected surface mass along any
line of sight will also be divergant\footnote{At large radius, $\Sigma_{\rm
nfw} \propto R^{-2}$, but the differential number of halos centred within an
annulus of width $\dee R$ is given by $\dee N_{\rm annulus} \propto R \dee R$,
so  $\Sigma_{\rm total} \propto \int_{0}^{\infty} R^{-1} \dee R$, which
diverges logarithmically}. Since infinite mass is unphysical, the profile must
be truncated at some point. \todo{Tom}{Add notes on previous truncation results}. Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low; \citet{NandraEtal2012} showed that the Universe's expansion can place an upper limit on the radius of NFW halos -- for cluster scale halos, this happens at around 25 times the NFW scale radius. In \Sref{sec:knownMh+z} we investigate how different truncations affect the recovered total convergence for a line of sight, using the truncated NFW profile of \citet{BMO}
\be\label{eq:bmoprofile}
\rho(r) = 
\frac{\rho_{\rm NFW} (r)}{1+\left(r/r_{t}\right)^2},
\ee
which is the same as the NFW profile in the limit that the truncation radius, $r_t$ goes to infinity. The convergence and shear for the BMO profile are given in Appendix \ref{appendix:halos}.

@@

We choose 100000 lines of sight from random positions in the catalogue, and for each line of sight we reconstruct the
convergences from every halo within 5 arcminutes and compare the reconstructed
$\kapparec$ with those from the ray tracing results. The standard deviation on $\kapparay$-$\kapparec$ is
shown in Figure \ref{fig:ScattervsTruncation} as a function of the radius at which the halo is truncated.
 It is clear from Figure \ref{fig:ScattervsTruncation} 
that as long as the truncation is greater than a few virial radii, the choice of truncation
radius does not broadly affect the scatter on $\kapparay-\kapparec$; from now on we choose 
to truncate the halos at $5 \Rhalo$. Since $\sigma\left(\kapparay-\kapparec\right)$ does not go to
zero, it is clear that out halo based prescription does not perfectly replicate the n-body results, we refer to this
 as the intrinsic error of the prescription.
 The intrinsic error has a standard deviation of $\sigi \sim 0.018$, although
this figure is inflated by a few outliers in the tails of $\pr\left(\kapparay-\kapparec\right)$. Such outliers would 
likely be rejected by their reconstructed shear not matching the shear of the lens model 
(see \citet{WongEtal2011} for the practicalities of this);
 this makes our estimate of the intrinsic error pessimistic. We do not include any additional constraints on P($\kappax$), given prior knowledge of the external shear in this work.

\begin{figure}
\includegraphics[width=\columnwidth]{figs/truncation_scatter.eps}
\caption[magcut]{The standard deviation in $\kapparec$ minus $\kapparay$ as a function of halo truncation radius in virial radii, using the truncated NFW profile of \citet{BMO}. In our models we truncate our halos at 5$R_{200}$}
\label{fig:ScattervsTruncation}
\end{figure}

@@

\begin{figure}
% \includegraphics[width=\columnwidth]{figs/perfectc.eps}
\caption[Biased?]{$\sumkappah$ verses $\kapparay$ for 100000 reconstructed lines of sight. $\sumkappah$ traces $\kapparay$, but with a non-zero offset which is due to the negative connvergence from voids. At fixed $\sumkappah$ the scatter in $\kapparay$ grows with $\sumkappah$.}
\label{fig:isitbiased}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figs/mag_scatter.eps}
\caption[magcut]{The 16, 50 and 84\% confidence intervals on $\kapparec$ minus $\kapparay$ as a function of the limiting $i$ band depth of the halo reconstruction. $\kapparec$ is given by $\sumkappah-\kappav$, where $\kappav$ is a constant such that $\left\langle\kapparec\right\rangle=0$. The majority of the constraining power comes from reconstructing halos with magnitudes between $18<i<24$}
\label{fig:magcut}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figs/radius_scatter.eps}
\caption[radius cut]{The 16, 50 and 84\% confidence intervals on $\kapparec$ minus $\kapparay$ as a function of the limiting radius (in arcminutes) beyond which halos are not reconstructed. The majority of the convergence comes from halos centred within an arcminute of the line of sight}
\label{fig:radcut}
\end{figure}

@@

We generate a stellar mass for each halo according to the stellar mass--halo mass relation of \citet{BehrooziEtal2010}. From this stellar mass we simulate 
an observed stellar mass by drawing a sample from $\pr(\log(M_{* \mathrm {obs}})|\log(M_{* \mathrm {true}}))$ which is given by \comments{ the product of the galaxy stellar mass function (GSMF) of \citet{Fontana2006} and} a Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$. Where a spectroscopic redshift exists stellar masses can be estimated with typical uncertainties of 0.15 dex \citep{xxx}, however with photometric redshifts stellar mass uncertainties are typically three times as large \citep{xxx}; we use $\sigma_{M_*}=0.15$ for halos with a spectroscopic redshift and $\sigma_{M_*}=0.45$ otherwise. \comments{The \citet{Fontana2006} GSMF is given by a Schechter function with redshift evolving parameters
\be
\label{eq:GSMF}
{\dee N \over \dee M_*} \propto \left(10^{(M_*-M_0(z))}\right)^{(1+\alpha(z))} \exp \left(-10^{(M_*-M_0(z))}\right)
\ee 
where $M_0(z)=11.16+0.17z-0.07z^2$ and $\alpha(z)=-1.18-0.082z$.} For photometric redshift errors we draw a redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take as a Gaussian of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where $z_{\rm spec}$ is the halo's true redshift in the \MS catalogue

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figs/cornerplot.eps}
\caption{68 \% and 95 \% contours of the joint distribution $\pr(\kapparay, \tilde\kappa_{\rm halos})$ given a mock reconstruction of our 40000 calibration lines of sight. $\tilde\kappa_{\rm halos}$ is the median of $\pr(\sumkappah)$ given a spectroscopic redshift for each halo. $\kapparay$ and $\tilde\kappa_{\rm halos}$ are strongly correlated, despite the blurring effect of uncertain halo masses.}
\label{fig:corner}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figs/widths.eps}
\caption{Widths of $\pr(\kappax)$ after applying our reconstruction of all halos down $to i=26$ and within 5 arcminutes of the line of sight. Results for 10000 lines of sight are shown. Green is for a reconstruction given perfect knowledge of halo mass and redshift, blue is for a reconstruction given a spectroscopic redshift for every halo, and red is for a reconstruction with photometric redshifts only. The dashed black line shows the width of the global $\pr(\kappax)$ distribution; the reconstruction process provides roughly a factor of 2 improvement for the majority of lines of sight. Spectroscopic redshifts improve the reconstruction, but at signifcant observational cost.}
\label{fig:width1}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figs/widths2.eps}
\caption{Widths of $\pr(\kappax)$ after a photometric reconstruction of all halos within different fields. The different field sizes and depths are given in the legend. As the field becomes smaller or shallower, fewer halos are being reconstructed and so the width of $\pr(\kappax)$ grows.}
\label{fig:width2}
\end{figure}

@@

The method we have outlined can also be used to estimate the external shear
along a line of sight. Shear is an observable that can be extracted from
strong lens modelling, however there is a degeneracy between internal and
external shear. Progress has been made in disentangelling external and
internal shear \citep[\eg][]{xxx} but there are still significant
uncertainties: \citet{WongEtal2011} attempted to match the shear from strong
lens models with a reconstruction of the local lens group environment, but
found a tension between the strong lens model and the reconstruction of the
environment. Since \citet{WongEtal2011} only reconstructed the local lens
group, rather than the full line of sight contribution, it is unclear whether
the external shear from lens models can be reconciled with a line of sight
reconstruction. {\it If} external shear can be measured, it provides an
additional constraint on which of the Millenium Simulation lines of sight are
similar to the reconstructed line of sight. \citet{SuyuEtal2012} found that
for RXJ1131 combining shear constriants with galaxy number count overdensity,
gave a significantly different $\pr(\kappax|\gamma,N_{45})$ copmpared to the
PDFfrom number count overdensity alone, $\pr(\kappax|N_{45})$.

@@

% \bibliographystyle{apj}
% \bibliography{references}
